Application-Level Regression Testing Framework using Jenkins

### 2017-03-29 manuscript/manuscript.tex

Jenkins nodes need to have a Java-based daemon (Jenkins' ''slave.jar``) to run which connects back to the master via a certain port (which is configurable). This can be considered a drawback. If the daemon somehow dies, it needs to be restarted. The daemon runs as regular user, the user which essentially runs the build and submits the jobs on the HPC system. In our case, we created a user called ''jenkins`` with the same privilege as any other regular user. Both the extra port opening and the daemon itself may be considered as attack vectors from a security perspective. At NICS however we consider this to be acceptable because of other mitigation (which we will discuss later).

@@

The benefit of this method is that it more closely mimicks the way real users access the HPC system. There is no need for an additional daemon to run on the HPC login nodes and there is no need for the corresponding opening of a port on the Jenkins VM. Because NCSA and NICS systems utilize two-factor RSA one-time password for user login, we needed to make slight modification so that Jenkins can have automated logins. The login node's \texttt{/etc/ssh/sshd_config} was modified to allow ''Public Key Authentication`` from the Jenkins VM unique IP address. Pairs of SSH keys with passphrase were generated on the Jenkins VM with their public keys deployed on the appropriate login nodes to allow for passwordless login. The SSH plugins allow one to manage which key (and passphrase) to use with which system. The keys on the Jenkins VM are located under the Jenkins home directory (by default \texttt{/var/lib/jenkins/.ssh}. Although configuring all of these can be somewhat tedious, once everything is set Jenkins should be able to run scripts on the intended HPC systems via SSH. For testing our setup, we created simple Jenkins projects whose task is to print out the \texttt{\$HOSTNAME} of the system.

@@

With this setup, all requests to the HTTP over SSL protocol (i.e. \texttt{https}) on port 443 by default) are forwarded to the Jenkins server and Jenkins responses are forwarded back to the client (i.e. web browser).

@@

\subsection{Security Considerations}
CUT THE NEXT TWO PARAGRAPHS AND DESCRIPTION OF CONFIG FILES OR REDUCE SINCE IT IS COVERED ABOVE --GALEN
Enabling Jenkins access to Blue Waters posed some unique security hurdles that we had to overcome. Blue Waters is an OTP only restricted access system. Jenkins has the ability to execute user-level commands on our login nodes. It also has some unfortunate default settings. The access control is set to "Jenkins' own user database," and the "Allow users to sign up" option is enabled, so if you don't have an account, you can create one by providing your name, e-mail and a password. Additionally, there's an authorization option enabled which says "Logged-in users can do anything." So, once signed in, you have full admin access to the Jenkins system instance.  This required us initially to test the deployment with our TDS. This resulted in the following requirement: restricted OTP access to the physical system hosting Jenkins. In addition, OTP only access to the Jenkins GUI command console must be contained within our IP space.  The Jenkins GUI will also restrict the command console access to our Blue Waters LDAP server.

\subsection{Configuration Choices}
The Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. The VM allows restricted host-based ssh access from two secure OTP only administrative systems. The Jenkins GUI presented additional challenges. The Jenkins GUI is configured to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. We restrict access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.  Jenkins is configured to listen on port 8080 by default and we restricted it to localhost only. A reverse proxy was configured to run Jenkins behind Apache HTTP Server and SSL for access to the administrative console. With this reverse proxy, apache accepts requests on port 80 and 443 of bwjenkins.ncsa.illinois.edu and forwards them to the Jenkins web server at localhost which is now firewall protected. Most of this configuration is in /etc/httpd/conf.d/ssl.conf. Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots. The Anonymous access view is not restricted. 
\begin{lstlisting}

NOTE: Install mod_authnz_external Apache package

(Jenkins sever configuration file snippets below)

/etc/ssh/sshd_config:
Match Host bwbh1.ncsa.illinois.edu,
bwbh2.ncsa.illinois.edu
HostbasedAuthentication yes

/etc/sysconfig/iptables:
-A INPUT -s 141.142.0.0/16 -m state --state NEW -m tcp 
-p tcp --dport 22 -j ACCEPT
-A INPUT -s 172.16.0.0/15 -m state --state NEW -m tcp 
-p tcp --dport 22 -j ACCEPT 
-A INPUT -m state --state NEW -m tcp -p tcp --dport 80 
-j ACCEPT
-A INPUT -s 141.142.0.0/16 -m state --state NEW -m tcp 
-p tcp --dport 443 -j ACCEPT

/etc/httpd/conf.d/ssl.conf:
 # -- The following sets ReverseProxy for Jenkins
ProxyRequests       Off
ProxyPreserveHost   On
AllowEncodedSlashes On
<Proxy *>
Order deny,allow
Allow from all
</Proxy>
ProxyPass       / http://localhost:8080/ nocanon
ProxyPassReverse / http://localhost:8080/
ProxyPassReverse / http://bwjenkins.ncsa.illinois.edu/
RequestHeader set X-Forwarded-Proto "https"
RequestHeader set X-Forwarded-Port "443"

 # -- OTP for Jenkins SSL connection
DefineExternalAuth pwauth+session pipe 
/usr/local/bin/pwauth+session
<LocationMatch / > 
AuthType Basic
AuthBasicProvider external
AuthName "NCSA RSA OTP login" 
AuthExternal pwauth+session
require valid-user  
RequestHeader unset "X-Forwarded-User"
RequestHeader set "X-Forwarded-User" (REMOTE_USER)
</LocationMatch>

/usr/local/bin/pwauth+session(OTP caching): 
https://github.com/reubendb/BasicAuthOTPSession
/blob/master/BasicAuthOTPSession.py#L1

/etc/pam.d/pwauth (for OTP):
 #%PAM-1.0
auth  required  /lib64/security/pam_securid.so
account  include  password-auth

/etc/sysconfig/jenkins (restrict to localhost):
JENKINS_PORT="8080"
JENKINS_LISTEN_ADDRESS=127.0.0.1
\end{lstlisting}
\subsection{LDAP with Jenkins} 
%To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, then select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
\caption{ Use LDAP with Jenkins }
\label{fig:LDAP-Jenkins}
\end{figure}
To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, then select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.\\
At first this failed because our LDAP is using a local CA.
WARNING: Failed to search LDAP for username, 
sun.security.provider.certpath.SunCertPathBuilderException:
unable to find valid certification path to requested target\\
\\
We had to add our certificate to the keystore:
/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
Enter keystore password: Trust this certificate? [no]:  yes\\
Certificate was added to keystore

\subsection{Configure Global Security}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
\caption{ Configure Global Security }
\label{fig:Configure-Global-Security}
\end{figure}
We are allowing access by username and LDAP groups. The permissions can be scoped for individuals and groups. An example is removing Job delete permissions to prevent one user or group from deleting each other's jobs.

>>>>

Jenkins nodes need to have a Java-based daemon (Jenkins' ''slave.jar``) to run which connects back to the master via a certain port (which is configurable). This can be considered a drawback. If the daemon somehow dies, it needs to be restarted. The daemon runs as regular user, the user which essentially runs the build and submits the jobs on the HPC system. In our case, we created a NICS user called ''jenkins`` with the same privilege as any other regular user. Both the extra port opening and the daemon itself may be considered as attack vectors from a security perspective. At NICS however we consider this to be acceptable because of other mitigation (which we will discuss later).

@@

The benefit of this method is that it more closely mimicks the way real users access the HPC system. There is no need for an additional daemon to run on the HPC login nodes and there is no need for the corresponding opening of a port on the Jenkins VM. Because NCSA and NICS systems utilize two-factor RSA one-time password for user login, one must make a slight modification so that Jenkins can have automated logins. The NCSA login node's \texttt{/etc/ssh/sshd_config} was modified to allow ''Public Key Authentication`` from the Jenkins VM unique IP address. We created an NCSA user called ''bwjenkins`` with standard user privilege. Pairs of SSH keys with passphrase were generated on the Jenkins VM with their public keys deployed on the appropriate login nodes in the bwjenkins user account to allow passwordless login. The SSH plugins allow one to manage which key (and passphrase) to use with which system. The keys on the Jenkins VM are located under the Jenkins home directory (by default \texttt{/var/lib/jenkins/.ssh}. Although this configuration can be somewhat tedious, when complete, Jenkins will be able to run scripts on the intended HPC systems via SSH. For testing our setup, we created simple Jenkins projects whose task is to print out the \texttt{\$HOSTNAME} of the system.

@@

In addition, we restrict connections to OTP using pwauth and session control which is also in the configuration file \texttt{/etc/httpd/conf.d/ssl.conf} inside the \texttt{<VirtualHost>} directive:
\begin{lstlisting}
# -- OTP for Jenkins SSL connection
DefineExternalAuth pwauth+session pipe 
/usr/local/bin/pwauth+session
<LocationMatch / > 
AuthType Basic
AuthBasicProvider external
AuthName "NCSA RSA OTP login" 
AuthExternal pwauth+session
require valid-user  
RequestHeader unset "X-Forwarded-User"
RequestHeader set "X-Forwarded-User" (REMOTE_USER)
</LocationMatch>
\end{lstlisting}

The session control was implemented with a custom python script available here:
\begin{lstlisting}
/usr/local/bin/pwauth+session(OTP caching): 
https://github.com/reubendb/BasicAuthOTPSession
/blob/master/BasicAuthOTPSession.py#L1
\end{lstlisting}

OTP is configured by \texttt{/etc/pam.d/pwath}: 
\begin{lstlisting}
 #%PAM-1.0
auth  required  /lib64/security/pam_securid.so
account  include  password-auth
\end{lstlisting}

With this setup, all OTP requests to the HTTP over SSL protocol (i.e. \texttt{https}) on port 443 by default) are forwarded to the Jenkins server and Jenkins responses are forwarded back to the client (i.e. web browser).

@@

%\subsection{Security Considerations}
%CUT THE NEXT TWO PARAGRAPHS AND DESCRIPTION OF CONFIG FILES OR REDUCE SINCE IT IS COVERED ABOVE --GALEN
%Enabling Jenkins access to Blue Waters posed some unique security hurdles that we had to overcome. Blue Waters is an OTP only restricted access system. Jenkins has the ability to execute user-level commands on our login nodes. It also has some unfortunate default settings. The access control is set to "Jenkins' own user database," and the "Allow users to sign up" option is enabled, so if you don't have an account, you can create one by providing your name, e-mail and a password. Additionally, there's an authorization option enabled which says "Logged-in users can do anything." So, once signed in, you have full admin access to the Jenkins system instance.  This required us initially to test the deployment with our TDS. This resulted in the following requirement: restricted OTP access to the physical system hosting Jenkins. In addition, OTP only access to the Jenkins GUI command console must be contained within our IP space.  The Jenkins GUI will also restrict the command console access to our Blue Waters LDAP server.

%\subsection{Configuration Choices}
%The Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. The VM allows restricted host-based ssh access from two secure OTP only administrative systems. The Jenkins GUI presented additional challenges. The Jenkins GUI is configured to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. We restrict access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.  Jenkins is configured to listen on port 8080 by default and we restricted it to localhost only. A reverse proxy was configured to run Jenkins behind Apache HTTP Server and SSL for access to the administrative console. With this reverse proxy, apache accepts requests on port 80 and 443 of bwjenkins.ncsa.illinois.edu and forwards them to the Jenkins web server at localhost which is now firewall protected. Most of this configuration is in /etc/httpd/conf.d/ssl.conf. Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots. The Anonymous access view is not restricted.

%\begin{lstlisting}
%NOTE: Install mod_authnz_external Apache package

%(Jenkins sever configuration file snippets below)

%/etc/ssh/sshd_config:
%Match Host bwbh1.ncsa.illinois.edu,
%bwbh2.ncsa.illinois.edu
%HostbasedAuthentication yes

%/etc/sysconfig/iptables:
%-A INPUT -s 141.142.0.0/16 -m state --state NEW -m tcp 
%-p tcp --dport 22 -j ACCEPT
%-A INPUT -s 172.16.0.0/15 -m state --state NEW -m tcp 
%-p tcp --dport 22 -j ACCEPT 
%-A INPUT -m state --state NEW -m tcp -p tcp --dport 80 
%-j ACCEPT
%-A INPUT -s 141.142.0.0/16 -m state --state NEW -m tcp 
%-p tcp --dport 443 -j ACCEPT

%/etc/httpd/conf.d/ssl.conf:
% # -- The following sets ReverseProxy for Jenkins
%ProxyRequests       Off
%ProxyPreserveHost   On
%AllowEncodedSlashes On
%<Proxy *>
%Order deny,allow
%Allow from all
%</Proxy>
%ProxyPass       / http://localhost:8080/ nocanon
%ProxyPassReverse / http://localhost:8080/
%ProxyPassReverse / http://bwjenkins.ncsa.illinois.edu/
%RequestHeader set X-Forwarded-Proto "https"
%RequestHeader set X-Forwarded-Port "443"

%\begin{lstlisting}
% # -- OTP for Jenkins SSL connection
%DefineExternalAuth pwauth+session pipe 
%/usr/local/bin/pwauth+session
%<LocationMatch / > 
%AuthType Basic
%AuthBasicProvider external
%AuthName "NCSA RSA OTP login" 
%AuthExternal pwauth+session
%require valid-user  
%RequestHeader unset "X-Forwarded-User"
%RequestHeader set "X-Forwarded-User" (REMOTE_USER)
%</LocationMatch>
 %
%
%/usr/local/bin/pwauth+session(OTP caching): 
%https://github.com/reubendb/BasicAuthOTPSession
%/blob/master/BasicAuthOTPSession.py#L1
%
 % 
%/etc/pam.d/pwauth (for OTP):
 %#%PAM-1.0
%auth  required  /lib64/security/pam_securid.so
%account  include  password-auth
%\end{lstlisting}
%/etc/sysconfig/jenkins (restrict to localhost):
%JENKINS_PORT="8080"
%JENKINS_LISTEN_ADDRESS=127.0.0.1
%\end{lstlisting}
\subsection{LDAP with Jenkins} 
%To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, then select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
\caption{ Use LDAP with Jenkins }
\label{fig:LDAP-Jenkins}
\end{figure}
To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, then select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.\\
At first this failed because our LDAP is using a local CA.
WARNING: Failed to search LDAP for username, 
sun.security.provider.certpath.SunCertPathBuilderException:
unable to find valid certification path to requested target\\
\\
We had to add our certificate to the keystore:
/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
Enter keystore password: Trust this certificate? [no]:  yes\\
Certificate was added to keystore

\subsection{Configure Global Security}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
\caption{ Configure Global Security }
\label{fig:Configure-Global-Security}
\end{figure}
We allow access by username and LDAP groups. The permissions can be scoped for individuals and groups. An example is removing Job delete permissions to prevent one user or group from deleting each other's jobs.
